Social Conditions of Fear

### 2023-11-29 scripts/manuscript.qmd
2 tables and 2 figures on gender&fear

library(tidyverse)
library(dplyr)
library(tidyr)
library(here)
library(rio)
library(janitor)
library(knitr)
library(kableExtra)
library(mice)
library(forcats)
library(ggplot2)
```

@@

>>>>

library(tidyverse)
library(dplyr)
library(tidyr)
library(here)
library(rio)
library(janitor)
library(knitr)
library(kableExtra)
library(mice)
library(forcats)
library(ggplot2)
library(vcd)
```

@@

# Tables and Figures

Let's understand our sample a little better. There are 2318 observations and 11 selected variables in our data set.

```{r}
#| label: descriptive statistics
view(gss_subset)

skimr::skim(gss_subset)

```{r}
#| label: table - gender and fear
gss_subset %>% 
  tabyl(fear, sexnow1) %>% 
  adorn_percentages() %>% 
  adorn_pct_formatting() %>% 
  adorn_ns(position = "front") %>% 
  adorn_title(
    row_name = "Fear at Night",
    col_name = "Gender",
    placement = "combined"
  ) %>% 
  flextable::flextable() %>% 
  flextable::autofit()
```

```{r}
#| label: table - racecombo and fear
gss_subset %>% 
  tabyl(fear, racecombo) %>% 
  adorn_percentages() %>% 
  adorn_pct_formatting() %>% 
  adorn_ns(position = "front") %>% 
  adorn_title(
    row_name = "Fear at Night",
    col_name = "Race",
    placement = "combined"
  ) %>% 
  flextable::flextable() %>% 
  flextable::autofit()
```

```{r}
#| label: fig1-fear_gender
#| fig-cap: Bar graph showing the proportion or respondants, by gender, that feared walking alone at night.

gss_subset %>% 
  ggplot(aes(x = sexnow1, y = after_stat(prop), group = fear, 
             fill = fear)) +
  geom_bar(position = "dodge") + 
  scale_y_continuous(labels = scales::percent) + 
  labs(title = "Social Fear by Gender",
       caption = "Question: Is there any area right around here--that is, within a mile--where you would be afraid to walk alone at night?",
       x = "Gender",
       y = NULL,
       fill = "Fear"
       ) +
  theme_bw()

```{r}
#| label: fig2-fear_gender
#| fig-cap: Bar graph showing the proportion or respondants, by gender, that feared walking alone at night.

gss_subset %>% 
  count(sexnow1, fear) %>% 
  ggplot() +
  geom_col(
    mapping = aes(x = fear,
                  fill = sexnow1,
                  y = n)
  ) +
  coord_flip() +
  labs(title = "Social Fear by Gender",
       caption = "Question: Is there any area right around here--that is, within a mile--where you would be afraid to walk alone at night?",
       x = "Count",
       y = "Fear",
       )
  theme_bw()
```
